The \dealii{} Library, Version 9.3

### 2021-06-20 9.3/paper.tex
Small addition to particles + funding

Additionally, the particle infrastructure now supports a faster search algorithm
for particles that moved farther than one cell width between particle sorting
operations, and support for updating ghost particles (particles that live in
ghost cells around the local domain) by updating their properties instead of
destroying and rebuilding their container. The latter step improves the
efficiency of ghost particle exchange significantly.

@@

>>>>

Additionally, the particle infrastructure now supports a faster search algorithm
for particles that moved farther than one cell width between particle sorting
operations, and support for updating ghost particles (particles that live in
ghost cells around the local domain) by updating their properties instead of
destroying and rebuilding their container. The latter step improves the
efficiency of ghost particle exchange significantly. With this feature,
\dealii can be used to generate scalable parallel code for Lagrangian
models such as the Discrete Element Method (DEM) \cite{golshan2021lethedem}
or Molecular Dynamics.

@@

B.~Blais was partially supported by the National Science and Engineering Research Council of Canada (NSERC)  through the RGPIN-2020-04510 Discovery Grant
